Enhancing instance-level constrained clustering through differential evolution

### 2018-12-23 Papers/SHADE/paperSHADE.tex
Terminado cuerpo paper SHADE

@@

\textcolor{red}{Citar a los de las hormigas}\\
\textcolor{red}{Poner un parrafo de aplicaciones del clustering con restricciones}

@@

\subsection{Short insertion to Differential Evolution}

To introduce Differential Evolution--from now on DE--we take as basis the review of the state-of-the-art performed by \cite{das2011differential}, where you can find a very detailed analysis on DE an its variants.

The first article written on differential evolution emerged in 1995 as a technical report written by \cite{noman2008differential}. From that moment on, DE's reputation was manifested in congresses and competitions where it was able to obtain competitive results that rivaled the state of the art of that moment. Specifically DE excelled in real optimization problems.

@@

@@

@@

Since we have the true labels associated to each of the datasets, we can use them in post-processing to evaluate the results provided by each method. We will use Adjusted Rand Index to measure the accuracy of the predictions resulting from each method we test \cite{hubert1985comparing}.Basic Rand Index computes de degree of agreement between two partitions $C_1$ and $C_2$ of a given dataset $X$. $C_1$ and $C_2$ are viewed as collections of $N(N - 1)/2$ pairwise decisions \cite{rand1971objective}.

>>>>

\textcolor{red}{Revisar que todos los subindices en los que aparecan comas lleven corchetes. Revisar que las asignaciones en los algoritmo sean flechas y no =}

@@

\textcolor{red}{Citar a los de las hormigas. Poner un parrafo de aplicaciones del clustering con restricciones}

@@

\subsection{Short Introduction to Differential Evolution}

\textcolor{red}{Eliminar toda la notacion matematica de esta seccion?}

To introduce Differential Evolution--from now on DE--we take as basis the review of the state-of-the-art performed by \cite{das2011differential}. You can also find in \cite{das2011differential} a very detailed analysis on DE an its variants.

The first article written on DE emerged in 1995 as a technical report written by \cite{noman2008differential}. From that moment on, DE's reputation was manifested in congresses and competitions where it was able to obtain competitive results that rivaled the state-of-the-art of that moment. Specifically DE excelled in real optimization problems.

@@

\subsection{(Classic) Resolution Methods}

\textcolor{red}{Clasicos clasicos no son}

Constrained clustering has many applications and has been widely studied in the literature. The first adaptation of a classic clustering method for constrained clustering was proposed by \cite{wagstaff2001constrained}. It involved modifying the widely studied K-medias algorithm to take into account instance level constraints, the already known ML and CL. This method was named COP-kmeans.

In \cite{antoine2012cecm} authors propose an adaptation of the evidential C-means algorithm, within the fuzzy clustering framework, for constrained clustering. The particularity of this resolution method is that the membership of instances to cluster is defined by a probabilistic belief function. This method redefines constraints from the point of view of belief functions and includes them in the cost function.

In \cite{pelleg2007k} LCVQE, a modification of CVQE (Constrained Vector Cuantization Error), is proposed. The adaptation of CVQE for constrained clustering was proven to produce high quality results, at the cost of a very high computational complexity. LCVQE (Linear CVQE) introduces a modification on CVQE objective function to make it more intuitive and less computationally complex. The experimentation resulted in a dramatic improvement on clustering quality over both noisy and clean constraints sets.

TVClust (Two Views Clustering) and RDP-means (Relation Dirichlet Process - Means) were prosed by \cite{khashabi2015clustering}. TVClust is able to incorporate the constraints to the clustering problem making a relaxed interpretation of them. The authors model the data set and constraints in different ways, perform clustering methods on them and try to find a consensus between both interpretations. Using this model as basis authors derive the deterministic algorithm RDP-means. This method can ve viewed as an extension of K-means that include side information (constraints) and has the property that the number of clusters ($K$) does not need to be specified.

\textcolor{red}{Decir que voy a comparar con ellos? Incluir mas métodos ``clasicos``?}

@@

\textcolor{red}{En esta seccion podria simplemente decir el numero de restricciones que genero como un numero magico sin meterme en nada de grafos, pero igual es un poco burro.}

@@

Since we have the true labels associated to each of the datasets, we can use them in post-processing to evaluate the results provided by each method. We will use Adjusted Rand Index to measure the accuracy of the predictions resulting from each method we test \cite{hubert1985comparing}. Basic Rand Index computes de degree of agreement between two partitions $C_1$ and $C_2$ of a given dataset $X$. $C_1$ and $C_2$ are viewed as collections of $N(N - 1)/2$ pairwise decisions \cite{rand1971objective}.
